\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.5in,top=0.45in,right=0.5in,bottom=0.45in]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{helvet}

% Set font to Helvetica (sans-serif)
\renewcommand{\familydefault}{\sfdefault}

% Color definitions
\definecolor{primary}{HTML}{1A365D}   % Deep navy for headings
\definecolor{textdark}{HTML}{2D3748}  % Dark grey for body text
\definecolor{accent}{HTML}{2B6CB0}    % Lighter blue for links/highlights

\color{textdark}

% Hyperlink configuration
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
    pdftitle={Muhammad Yahya Azeem - Resume},
    pdfauthor={Muhammad Yahya Azeem}
}

% Page style configuration
\pagestyle{empty}

% Section formatting
\titleformat{\section}
  {\color{primary}\normalfont\Large\bfseries}
  {}{0em}
  {}
  [{\color{accent}\titlerule[1pt]\vspace{3pt}}]

\titlespacing*{\section}{0pt}{10pt}{4pt}

% Global itemize settings
\setlist[itemize]{leftmargin=*,noitemsep,topsep=2pt,parsep=1pt,partopsep=0pt,itemsep=2pt}

% Custom commands
\newcommand{\project}[4]{
    \noindent\textbf{\href{#4}{\color{primary}#1}} \hfill \textit{#2} \\
    \noindent\textit{Key Technologies: #3}
}

\newcommand{\achievement}[2]{
    \noindent\textbf{\color{primary}#1} \hfill \textit{#2}
}

\begin{document}

% ==================== HEADER ====================
\begin{center}
    {\Huge\bfseries\color{primary} Muhammad Yahya Azeem} \\
    \vspace{3pt}
    \small
    Irving, Texas $\cdot$ +1 (945) 246-0159 $\cdot$ \href{mailto:yahyaazeem44@gmail.com}{yahyaazeem44@gmail.com} $\cdot$ \href{https://github.com/yahya-azeem}{github.com/yahya-azeem} \\
    \vspace{2pt}
    \href{https://www.linkedin.com/in/muhammad-azeem-474612357/}{linkedin.com/in/muhammad-azeem-474612357} $\cdot$ 
    \href{https://profile.hackthebox.com/profile/019c6962-e472-7141-bfee-10910c4881e8}{HTB Profile}
\end{center}

\vspace{-4pt}

% ==================== PROFILE ====================
\section*{Professional Summary}
Software and security researcher specializing in systems programming, emulation layers, machine learning optimization, and offensive security.

% ==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}
\noindent\textbf{Programming Languages:} Rust, C, C++, Python, TypeScript, Shell, Assembly. \\
\noindent\textbf{Systems \& Architecture:} OS Kernel Development, Virtual Memory Management, Vulkan SDK, Systems Virtualization. \\
\noindent\textbf{Deep Learning \& Optimization:} Transformer Architecture Design, Custom Optimizers, Quantization, PyTorch, NumPy. \\
\noindent\textbf{Offensive Security:} Exploit Development, Kernel-level Exploitation, Reverse Engineering, Binary Analysis, Network Auditing.

% ==================== EXPERIENCE ====================
\section*{Professional Experience}
\achievement{Cybervigilance LLC — Technology Risk Management \& Cybersecurity Intern}{Oct 2025 -- Present}
\begin{itemize}
    \item \textbf{GRC \& Risk Management:} Delivered 3 risk assessments and corporate presentations aligned with NIST frameworks and ISO 27001 standards for multi-million and billion-dollar entities.
\end{itemize}

% ==================== CYBERSECURITY ACHIEVEMENTS ====================
\section*{Cybersecurity \& Offensive Capabilities}
\achievement{Hack The Box (HTB) — Rooted ``Cobblestone'' Machine (Insane Difficulty)}{June 2026}
\begin{itemize}
    \item \textbf{Active Exploitation:} Compromised and rooted the machine in 3 days utilizing binary analysis and custom payload bypasses.
\end{itemize}

% ==================== PROJECTS ====================
\section*{Projects}

\project{ShadPS5 — PlayStation 5 Emulator}{June 2026}{Rust, Vulkan 1.3, SDL2, ash}{https://github.com/yahya-azeem/ShadPS5}
\begin{itemize}
    \item \textbf{ELF/SELF Loader \& Linker:} Designed the loader in Rust, translating 200+ Cryptographic Name Identifiers (NIDs) to initialize guest library imports.
    \item \textbf{GPU Shader Translation:} Engineered a translation engine mapping 50+ guest shader instructions to host-native Vulkan SPIR-V bytecode to render 3D geometry.
\end{itemize}

\vspace{6pt}

\project{Project Golf Ball — OpenAI Parameter Golf LLM Optimizer}{April 2026}{Python, PyTorch, CUDA}{https://github.com/yahya-azeem/Project-Golf-Ball}
\begin{itemize}
    \item \textbf{11-Layer Transformer Model:} Optimized an 11-layer language model (512-dim) trained on 100M+ FineWeb tokens to fit strictly within a 16MB artifact limit.
\end{itemize}

\vspace{6pt}

\project{Polymarket Copytrade Bot}{May 2026}{Rust, Tokio, WebSockets, CLOB}{https://github.com/yahya-azeem/polymarket-copy-bot-rust}
\begin{itemize}
    \item \textbf{Asynchronous Copytrading Engine:} Developed a Rust/Tokio system to mirror Whale orders with sub-5ms latency, protecting capital with a 20\% daily drawdown threshold.
\end{itemize}

\vspace{6pt}
\noindent\textbf{Other Projects:} \textbf{\href{https://github.com/yahya-azeem/Unixy-System}{\color{primary}Unixy-System}} (custom OS kernel in C/Assembly supporting x86/MIPS/PowerPC) $\cdot$ \textbf{\href{https://github.com/yahya-azeem/Protection-Valley}{\color{primary}Protection Valley}} (SvelteKit 5 e-commerce platform with a Vercel-deployed Rust serverless backend).

% ==================== EDUCATION ====================
\section*{Education}
\noindent\textbf{\color{primary}The University of Texas at Dallas} \hfill \textit{2026 -- 2030} \\
Bachelor of Science in Computer Science \hfill \textit{Richardson, Texas}

\end{document}
